Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-17 paper/high-assurance-contracts.tex
Update example contracts

    -- start user definitions
    const MAX_LATENCY : int = 1; *\label{line:mon-const}*

@@

    eq policy : bool = (rsp => req) -> *\label{line:mon-policy}*
                         (    (isPending => latency < MAX_LATENCY)   
                          and (rsp => (req or pre(isPending))));

    assume "One outstanding request at a time" : *\label{line:mon-assume}*
      (true -> (req => not pre(isPending))); 
    -- stop user definitions

@@

The AGREE specification for the monitor is shown in \figref{fig:monitor} and is considerably more complex than the filter.
BriefCASE generates everything but the statements in \linesref{line:mon-const}{line:mon-assume}.
As with the filter, the guarantees completely define the output, as required for synthesis, in terms of the policy and the alert.
The \texttt{alert} variable defined on \lineref{line:mon-alert} depends not just on the policy but also on the indicated behavior from the BriefCASE dialogue box. 
Marking \texttt{is\_latched} as true makes the alert persistent, meaning that once the alert is raised, it is always raised; otherwise, it is the complement of the policy value in the current step.

@@

The policy definition only works if there is never more than one outstanding request at a time.
That requirement is encoded in the assumption on \lineref{line:mon-assume}.
A request is only allowed if one is not already pending in the pre-state of the component.
The policy can be written without needing the assumption, but it is much simpler to write with the assumption.

>>>>

    -- start user definitions
    assume "One automation request in flight at a time" : *\label{line:mon-assume}*
      true -> (req => pre(Historically(not req) or Since(not req, rsp)));

    const MAX_LATENCY : int = 1; *\label{line:mon-const}*

@@

    eq policy : bool = (rsp => req) -> *\label{line:mon-policy}*
                         (    (isPending => latency < MAX_LATENCY)   
                          and (rsp => (req or pre(isPending))));
    -- stop user definitions

@@

The AGREE specification for the monitor is shown in \figref{fig:monitor} and is considerably more complex than the filter.
BriefCASE generates everything but the statements in \linesref{line:mon-assume}{line:mon-policy}.
As with the filter, the guarantees completely define the output, as required for synthesis, in terms of the policy and the alert.
The \texttt{alert} variable defined on \lineref{line:mon-alert} depends not just on the policy but also on the indicated behavior from the BriefCASE dialogue box. 
Marking \texttt{is\_latched} as true makes the alert persistent, meaning that once the alert is raised, it is always raised; otherwise, it is the complement of the policy value in the current step.

@@

The policy definition only works if there is never more than one outstanding request at a time; otherwise, the latency counter resets incorrectly.
That requirement is encoded in the assumption on \lineref{line:mon-assume} and is the same assumption used for the system input.
The policy can be written without needing the assumption, but it is much simpler to write with the assumption.

### 2022-03-17 paper/sw-contract.tex
Update example contracts

guarantee "Waypoints coincide with air vehicle locations": *\label{line:sw-guarantee-1}*
  wp => avl;
guarantee "Starts include a new waypoint" : *\label{line:sw-guarantee-2}*
  strt => wp;
guarantee "Waypoints are well-formed" :  *\label{line:sw-guarantee-3}*
  wp => WELL_FORMED_WAYPOINT(Waypoint);
guarantee "Starts within one cycle of requests if not alerting" : *\label{line:sw-guarantee-4}*
  (strt => ((not alrt) and req)) -> 
  (strt => ((not alrt) and (req or pre(req))));
guarantee "Alert if not started within one cycle of requests" : *\label{line:sw-guarantee-5}*
    true -> ((pre(req and not strt) and not strt) => alrt);
guarantee "Once alerted always alerted" : *\label{line:sw-guarantee-6}*
  not alrt or (Once(alrt) and alrt);
\end{lstlisting}
\end{lrbox}

@@

\lineref{line:sw-guarantee-5} forces the alert to sound if the start does not arrive within the one-step bound.
Together with \lineref{line:sw-guarantee-4} the contract model allows for non-alerting and alerting behavior.
The final guarantee on \lineref{line:sw-guarantee-6} defines additional behavior for the alert.

The \texttt{Once} operator is true if the enclosed expression has ever been true before the current moment.
\lineref{line:sw-guarantee-6} ensures that once alerted always alerted because either there has never been an alert, \texttt{\textbf{not} alrt}, or there has been an alert sometime in the past and so it is alerting now, \texttt{\textbf{Once}(alrt) \textbf{and} alrt}.
These six guarantees define the behavior of the SW component under the three assumptions.

>>>>

guarantee "Waypoints coincide with air vehicle locations": *\label{line:sw-guarantee-1}*
  wp => avl;
guarantee "Starts include a new waypoint" : *\label{line:sw-guarantee-2}*
  strt => wp;
guarantee "Waypoints are well-formed" :  *\label{line:sw-guarantee-3}*
  wp => WELL_FORMED_WAYPOINT(Waypoint);
guarantee "Starts within one cycle of requests if not alerting" : *\label{line:sw-guarantee-4}*
  (strt => ((not alrt) and req)) -> 
  (strt => ((not alrt) and (req or pre(req))));
guarantee "Alert if not started within one cycle of requests" : *\label{line:sw-guarantee-5}*
  true -> ((pre(req and not strt) and not strt) => alrt);
guarantee "Once alerted always alerted" : *\label{line:sw-guarantee-6}*
  true -> (pre(alrt) => alrt);
\end{lstlisting}
\end{lrbox}

@@

\lineref{line:sw-guarantee-5} forces the alert to sound if the start does not arrive within the one-step bound.
Together with \lineref{line:sw-guarantee-4} the contract model allows for non-alerting and alerting behavior.
\lineref{line:sw-guarantee-6} ensures that once alerted always alerted since an alert in the pre-state requires an alert in the post-state., \texttt{\textbf{Once}(alrt) \textbf{and} alrt}.
These six guarantees define the behavior of the SW component under the three assumptions.
